### 2021-03-23 input/figproof.tex
reworkd figures of proofs

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$'s may stop up-to-date $\alpha$'s
    from reaching all processes that require it along the shortest path from $a$ to $c$.
    To solve this issue, we must guarantee
    the eventual removal of stale $\alpha$'s (see Figure~\ref{fig:proofB}).]
    {\input{input/figproofA.tex}}
    \hspace{10pt}
    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$'s may stop $\delta$'s from reaching
    processes with targeted $\alpha$'s. To ensure correctness, $b$ must either
    deliver $\delta_d$, $\delta_d^{0.5}$, or another $\alpha$, as well as downstream processes
    that delivered $\alpha$ coming from $b$ such as $g$.]
    {\input{input/figproofB.tex}}
    \caption{\label{fig:proof}Dynamic partitioning leads to correctness issues due to
      staleness and ordering of operations.}
  \end{center}
\end{figure*}

>>>>

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:proofA}Stale $\alpha$'s may stop
      other $\alpha$'s from reaching all processes ($b$ and $c$) that
      require it along the shortest path. Hence, we must guarantee
      eventual purging of stale $\alpha$'s (see
      Figure~\ref{fig:proofB}).]  {\input{input/figproofA.tex}}
    \hspace{10pt}
    \subfloat[Part B][\label{fig:proofB}Stale $\alpha$'s may
      stop $\delta$'s from reaching
      processes with targeted $\alpha$'s.
      To ensure consistent partitioning, $b'$ and $b''$
      must remove $\alpha_{d}$ either by delivering $\delta_d$,
      or a more specific $\delta_d^{0.5}$ and $\delta_d^{1.5}$ respectively.]
    {\input{input/figproofB.tex}}
    \caption{\label{fig:proof}Dynamic partitioning leads to correctness issues due to
      staleness and ordering of operations.}
  \end{center}
\end{figure*}

### 2021-03-23 input/figproofA.tex
reworkd figures of proofs

  \newcommand\X{50pt}
  \newcommand\Y{-45pt}

@@

  \draw[opacity=0] (-2*\X, 0) -- (3*\X, 0);

@@

  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% b - ...

  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% ... - c

  \draw[->] ( 0, \Y + 5pt) -- ( 0, -5pt); %% ... - b

  \draw[->] ( -\X + 5pt, \Y ) -- ( -5pt, \Y); %% d - ...

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (2*\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw[fill=white] ( 0, \Y) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (-\X, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
  \draw ( 0, 5pt) node[above, color=\PC]{$\ADD_d^{0.5}$};
  \draw (2*\X, 5pt) node[above]{expect \textcolor{\PA}{$\alpha_a$}};

  \draw (-\X, \Y + 5pt) node[above, color=\PC]{$\DEL_d$};

>>>>

  \newcommand\X{70pt}
  \newcommand\Y{-40pt}

@@

  \draw[opacity=0] (-1.5*\X, 0) -- (1.5*\X, 0);

  \draw[<->] (-5pt - \X, -\Y) -- node[above]{I} (5pt, -\Y); %% I

@@

  \draw[<->] (-5pt, 5pt -\Y) -- node[above]{II} (5pt + \X, 5pt -\Y); %% II
  \draw[->] (0 + 5pt, 0) -- (-5pt +  \X, 0); %% b - c

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
  \draw ( 0, 5pt) node[above, color=\WRONG]{$\ADD_d^{0.5}$};
  \draw (\X,-5pt) node[below, font=\scriptsize]{expect \textcolor{\PA}{$\alpha_a$}};
  \draw (0, -5pt) node[below, font=\scriptsize]{expect $\textcolor{\PC}{\DEL_d} \rightarrow \textcolor{\PA}{\alpha_a}$};

### 2021-03-23 input/figproofB.tex
reworkd figures of proofs

  \draw[->] (-\X + 5pt, 0) -- node[above, font=\small, color=\PC]{$\DEL_d$} (0 - 5pt, 0); %% d - e

  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - ...

  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% ... - b

  \draw[->] ( 0, \Y + 5pt) -- ( 0, -5pt); %% ... - e

  \draw[->] ( -\X + 5pt, \Y ) -- ( -5pt, \Y); %% f - ...

  \draw[->] ( 5pt, \Y) -- ( \X - 5pt, \Y); % ... - ...

  \draw[->] ( \X + 5pt, \Y + 5pt ) -- ( 2*\X - 5pt, -5pt); % ... - b

  \draw[->] ( 2*\X + 5pt, 0 ) -- ( 3*\X - 5pt, 0); % b - g

  \draw[fill=white] (-\X, 0) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (2*\X, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw[fill=white] ( 0, \Y) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (-\X, \Y) node{$\bm{f}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw[fill=white] ( \X, \Y) node{$\ldots$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw[fill=white] ( 3*\X, 0) node{$\bm{g}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PC]{$\DEL_d$};
  \draw ( 0, 5pt) node[above, color=\PB]{$\ADD_f^{0.5}$};
  \draw (2*\X, 5pt) node[above, align=center]{expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{0.5}}$\\$\textcolor{\PB}{\ADD_f^1} \rightarrow \textcolor{\PB}{\DEL_f} \rightarrow \textcolor{\PC}{\ADD_d^{0.5}}$};

  \draw (-\X, \Y + 5pt) node[above, color=\PB]{$\DEL_f$};

  \draw (3*\X, -5pt) node[below, align=center]{$\textcolor{\PC}{\ADD_d^{1.5}}$\\expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{1.5}}$};

>>>>

  \draw[opacity=0] (-1.5*\X, 0) -- (2.5*\X, 0);

  \draw[<->] (-5pt - \X, -\Y) -- node[above]{III} (5pt, -\Y); %% III    
  \draw[->] (-\X + 5pt, 0) -- node[above, font=\small, color=\PC]{$\DEL_d$} (0 - 5pt, 0); %% d - e

  \draw[<->] (-5pt , 5pt -\Y) -- node[above]{IV} (5pt + \X, 5pt -\Y); %% IV
  \draw[->] (0 +5pt, 0) -- (\X -5pt, 0); %% e - b'

  \draw[<->] (-5pt + \X , 10pt -\Y) -- node[above]{V} (5pt + 2*\X, 10pt -\Y); %% V
  \draw[->] ( \X +5pt, 0) -- (2*\X -5pt, 0); %% b - b''

  \draw[fill=white] (-\X, 0) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{b'}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (2*\X, 0) node{$\bm{b''}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PC]{$\DEL_d$};

  \draw ( 0, 5pt) node[above, color=\WRONG]{$\ADD_f^{0.5}$};
  \draw ( 0, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PB}{\DEL_f}$};

  \draw ( \X, 5pt) node[above]{$\textcolor{\PB}{\ADD_f^1} \rightarrow \textcolor{\PB}{\DEL_f} \rightarrow \textcolor{\PC}{\ADD_d^{0.5}}$};
  \draw ( \X, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{0.5}}$};

  \draw (2*\X, 5pt) node[above]{$\textcolor{\PC}{\ADD_d^{1.5}}$};
  \draw (2*\X, -5pt) node[below, font=\footnotesize]{expect $\textcolor{\PC}{\DEL_d}$ or $\textcolor{\PC}{\DEL_d^{1.5}}$};

### 2021-03-23 input/proposal.tex
reworkd figures of proofs

\input{input/figdel.tex} %% figure positioning

@@

\begin{definition}[\TODO{Adaptive scope}]
  Eventual consistent partitioning in presence of dynamic
  partitioning. Eventually get the last partition, eventually remove
  all outdated control information.
\end{definition}

>>>>

%% \input{input/figdel.tex} %% figure positioning

@@

\begin{theorem}[Dynamic consistent partitioning]
  Eventual consistent partitioning in presence of dynamic sources
  requires
  \begin{inparaenum}[(i)]
  \item eventual purging of stale notifications, and
  \item eventual delivery of bests partitions.
  \end{inparaenum}
\end{theorem}

\begin{proof}
\TODO{Meow meow meow.}
\end{proof}
